Classless Java

### 2015-11-19 paper/sections/Implementation.tex
section5 Implementation revised

\section{Implementation}
\begin{comment}
Haoyuan

discuss implementation in lombok; and limitations.

\bruno{The implementation does not support separate compilation yet. Can we fix this?}

\haoyuan{http://notatube.blogspot.hk/2010/12/project-lombok-creating-custom.html}

\haoyuan{https://blog.frankel.ch/lombok-reduces-your-boilerplate-code}

\haoyuan{https://projectlombok.org/}
\end{comment}

@@

The biggest reasons to use Lombok rather than using conventional Java annotation
processor is
\begin{itemize}
%this seamd like a commercial spot
%\item Lombok is byte-code based instead of source-code based, which makes client
%  code concise and easy to maintain. Such code generation is performed at
%  compile time to modify bytecode.
\item Lombock modify the generation process of the class files.
neither the source code is modified nor new  Java files are generated.
\item Moreover, and probably more importantly, Lombok is capable of generating
  code \emph{inside} a class/interface.This is the ability that conventional
  Java annotation processor do not provide.
\end{itemize}

Our prototype implementation using Lombok has certain limitation: 
\begin{itemize}
\item We do not support separate compilation yet at this
  stage, for in the implementation it is hard to capture a type declaration from
  its reference.
\item At this stage our implementation only realizes the Eclipse handler and our experiments are all conducted in Eclipse.
\end{itemize}

>>>>

\section{Implementation}

@@

 The biggest reasons to use Lombok rather than using a conventional Java
 annotation processor are:
\begin{itemize}
%this seamd like a commercial spot
%\item Lombok is byte-code based instead of source-code based, which makes client
%  code concise and easy to maintain. Such code generation is performed at
%  compile time to modify bytecode.
\item Lombok modifies the generation process of the class files. Neither the
  source code is modified nor new Java files are generated.
\item Moreover, and probably more importantly, Lombok is capable of generating
  code \emph{inside} a class/interface.This is the ability that conventional
  Java annotation processor do not provide.
\end{itemize}

\paragraph{Limitation}
Our prototype implementation using Lombok has certain limitation: 
\begin{itemize}
\item The prototype does not support separate compilation yet. Currently all
  related interfaces have to appear in a single Java file. Therefore, changes to
  a single interface would require re-compiling the whole file. This compilation
  limitation is not caused by our algorithm. It is Lombok implementation related
  issue: in Lombok it is hard to capture a type declaration from its reference,
  even harder when the type declaration is in other files (we have not found a
  way to do this currently).
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse. The implementation for
  \texttt{javac} is missing.
\end{itemize}

\paragraph{Comparison with other Lombok annotations}
Lombok project provides a set of predefined annotations, including constructor
generators similar as ours (e.g., \textbf{@NoArgsConstructor},
\textbf{@RequiredArgsConstructor} and \textbf{@AllArgsConstructor}). They
generate various kinds of constructors for \emph{classes}, with or without
constructor arguments. This set of annotations is of great use, especially when
used together with other features provided in Lombok (e.g.,
\textbf{@Data}). Moreover, the implementation of these annotations in Lombok
gives us hints on how to implement \mixin. However, none of these annotations
can model what we are doing with \mixin - generating constructor-methods
(\textbf{of}) for \emph{interfaces}. Apart from constructors, \mixin also
provides other convenient features (including generating fluent setters, type
refinement,etc) which the base Lombok project could not provide.
